DeepSphere: a graph-based spherical CNN

### 2019-09-23 main.tex
precisions in climate tables

* icosahedron dataset from \cite{jiang2019sphericalcnn} \\
* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
* cross entropy loss between parenthesis\\
* 5 runs for each loss to obtain mean and std\\
* same architecture as gauge, more feature maps than Jiang\\
* perf with same arch as Jiang in appendix => not enough channels!\\
* even more feature maps give us one more point in perf\\
* cannot compare with Mudigonda: not the same input data\\
* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling

@@

The proof of this result is instructive since it shows that we need to impose some regularity conditions on the sampling. If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$. If the sampling is not equal area, meaning that in general $A_i\neq A_j$, it can be shown that we need a slightly more complex condition: $\max_{i=0,\dots,n-1}d_iA_i\leq Cn^{-\frac{3}{2}}$.\\
In the work of Belkin et al. \cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn. In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.

To conclude, we can see that the result obtained has the same form than the result obtained in \cite{belkin2005towards}. Given the kernel density $t(n)=n^\beta$, if Belkin et al. proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the HEALPix case for $\beta \in (-\frac{1}{5}, 0)$. This kind of result can be interpreted in the following way. In order to have this pointwise convergence, we need to reduce the kernel width but \textit{not so fast} compared to the resolution of the graph. In other words, the kernel width has to be reduced but is somewhat limited by the resolution of the graph. In the next section we'll see how to set in practice a good kernel width $t$ given a graph resolution $n$.
\begin{remark}
	Pointwise convergence is just a necessary condition for spectral convergence.  Theorem \ref{theo:pointwise convergence in the healpix case} does not imply convergence of eigenvalues and eigenvectors.
\end{remark}

@@

* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
* DS-optimal has 2 times the number of feature maps of DS. \\
* \todo{What is DS and DS-Cohen?} \\
* \todo{Is (equi non-weighted) the full resolution?} \\
* \todo{check column order for DS} \\

\begin{table}
    \centering
	\begin{tabular}{l l l l l}
		\toprule
        & TC & AR & BG & mean \\
		\midrule
		\cite{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
		\cite{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
		\cite{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
        \cite{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
        \cite{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
		\midrule
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 \\
        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 \\
		\midrule
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 \\
        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 \\
		\midrule
		\todo{DS-Cohen (weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DS-Cohen (non-weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DeepSphere (equi non-weighted)} & 31.3 & 75.2 & 99.9 & 68.80 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: accuracy.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes, against the background (BG).
		\todo{\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.}
		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l l l l}
		\toprule
        & TC & AR & mean \\
		\midrule
		\cite{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
        \cite{cohen2019gauge} (S2R) & - & -& 68.6 \\
        \cite{cohen2019gauge} (R2R) & - & -& 75.9 \\
		\midrule
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 \\
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 \\
		\midrule
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 \\
        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 \\
		\midrule
		\todo{DS-Cohen (weighted)} & 13.1 & 80.3 & 46.7 \\
		\todo{DeepSphere (equi non-weighted)} & 55.53 & 94.85 & 75.19 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: average precision.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes.
		Note that a weighted cross-entropy loss is not optimal for the average precision metric.
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l r r r}
		\toprule
		& \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
        \cmidrule(lr){2-2} \cmidrule(lr){3-4}
		& params & inference & training \\
		\midrule
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
		\cite{jiang2019sphericalcnn} & 330\,k & 10\,ms & 10\,h \\ % 328'339
		% \cite{cohen2019gauge} (S2R) & - & - & - \\
        % \cite{cohen2019gauge} (R2R) & - & - & - \\
		DeepSphere (Jiang) & 590\,k & 5\,ms & 3\,h \\ % 590k
        DeepSphere & 13\,M & 33\,ms & 13\,h \\ % 12'926'432
		DeepSphere (optimal) & 52\,M & 50\,ms & 20\,h \\
		\todo{DS-Cohen (weighted)} & 2\,M & 11\,ms & 4\,h \\
		\todo{DeepSphere (equi non-weighted)} & - & 567\,ms & 48\,h \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: size and speed.
	}
\end{table}

>>>>

* icosahedron dataset from \cite{jiang2019sphericalcnn} \\
* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
* cross entropy loss between parenthesis\\
* 5 runs for each loss to obtain mean and std\\
* same architecture as gauge, more feature maps than Jiang\\
* perf with same arch as Jiang in appendix => not enough channels!\\
* even more feature maps give us one more point in perf\\
* need more feature maps and layers to compensate for isotropy \\
* cannot compare with Mudigonda: not the same input data\\
* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling

@@

The proof of this result is instructive since it shows that we need to impose some regularity conditions on the sampling. If the sampling is equal area as HEALPix, meaning that all the patches $\sigma_i$ have the same area, then we need to impose that $ d^{(n)}\leq \frac{1}{\sqrt{n}}$. \\
In the work of \cite{belkin2005towards} the sampling is drawn form a uniform random distribution on the sphere, and their proof heavily relies on the uniformity properties of the distribution from which the sampling is drawn. In our case the sampling is deterministic, and the fact that for a sphere there doesn't exist a regular sampling with more than 12 points (the vertices of a icosahedron) is indeed a problem that we need to overcome by imposing the regularity conditions above.

To conclude, we can see that the result obtained has the same form than the result obtained in \cite{belkin2005towards}. Given the kernel density $t(n)=n^\beta$, if Belkin et al. proved convergence in the random case for $\beta \in (-\frac{1}{4}, 0)$, we proved convergence in the deterministic case for $\beta \in (-\frac{1}{5}, 0)$. This kind of result can be interpreted in the following way. In order to have this pointwise convergence, we need to reduce the kernel width but \emph{not so fast} compared to the resolution of the graph. In other words, the kernel width has to be reduced but is somewhat limited by the resolution of the graph.

@@

* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
* DS-optimal has 2 times the number of feature maps of DS. \\
* \todo{What is DS and DS-Cohen?} DS has 4 times more feature maps and one more layer than DS-Jiang. DS-optimal has still 2 times more feature maps. DS-Cohen should be mostly gauge (based on paper, no code): 4 times more feature maps, but 2 layers less than DS-Jiang. \\
* \todo{Is (equi non-weighted) the full resolution?} Yes, but less feature maps and layers. Can run, but not enough GPU memory for an optimal architecture. \\
* \todo{check column order for DS} \\

\begin{table}
    \centering
	\begin{tabular}{l l l l l}
		\toprule
        & TC & AR & BG & mean \\
		\midrule
		\cite{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
		\cite{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
		\cite{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
        \cite{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
        \cite{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
		\midrule
		DS (Jiang architecture, weighted loss) & 97.1 & 97.6 & 96.5 & 97.1 \\
        DS (weighted loss) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
		DS (wider architecture, weighted loss) & 91.5 & 93.4 & 99.0 & 94.6 \\
		\midrule
        DS (Jiang architecture, non-weighted loss) & 33.6 & 93.6 & 99.3 & 75.5 \\
        DS (non-weighted loss) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
        DS (wider architecture, non-weighted loss) & 73.4 & 92.7 & 99.8 & 88.7 \\
		\midrule
		\todo{DS (Cohen architecture, weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DS (Cohen architecture, non-weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DS (full dataset, non-weighted loss)} & 31.3 & 75.2 & 99.9 & 68.80 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: accuracy.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes, against the background (BG).
		\todo{\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.}
		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l l l l}
		\toprule
        & TC & AR & mean \\
		\midrule
		\cite{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
        \cite{cohen2019gauge} (S2R) & - & -& 68.6 \\
        \cite{cohen2019gauge} (R2R) & - & -& 75.9 \\
		\midrule
        DS (Jiang architecture, non-weighted loss) & 46.2 & 93.9 & 70.0 \\
        DS (non-weighted loss) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
        DS (wider architecture, non-weighted loss) & 84.71 & 98.05 & 91.38 \\
		\midrule
        DS (Jiang architecture, weighted loss) & 49.7 & 89.2 & 69.5 \\
        DS (weighted loss) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
        DS (wider architecture, weighted loss) & 52.80 & 94.78 & 73.79 \\
		\midrule
		\todo{DS (Cohen architecture, weighted loss)} & 13.1 & 80.3 & 46.7 \\
		\todo{DS (full dataset, non-weighted loss)} & 55.53 & 94.85 & 75.19 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: average precision.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes.
		Note that a weighted cross-entropy loss is not optimal for the average precision metric.
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l r r r}
		\toprule
		& \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
        \cmidrule(lr){2-2} \cmidrule(lr){3-4}
		& params & inference & training \\
		\midrule
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
		\cite{jiang2019sphericalcnn} & 330\,k & 10\,ms & 10\,h \\ % 328'339
		% \cite{cohen2019gauge} (S2R) & - & - & - \\
        % \cite{cohen2019gauge} (R2R) & - & - & - \\
		DeepSphere (Jiang architecture) & 590\,k & 5\,ms & 3\,h \\ % 590k
        DeepSphere & 13\,M & 33\,ms & 13\,h \\ % 12'926'432
		DeepSphere (wider architecture) & 52\,M & 50\,ms & 20\,h \\
		\todo{DS (Cohen architecture)} & 2\,M & 11\,ms & 4\,h \\
		\todo{DS (full dataset)} & - & 567\,ms & 48\,h \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: size and speed.
	}
\end{table}
